Declarative runtime reconfiguration of pulverised distributed systems \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-10 paper-2023-acsos-pulverization.tex
Comment on rw

ADSL (AWaRE DSL)~\cite{DBLP:conf/aswec/ChhetriLUVKNR18/adsl} % and see corresp RW

>>>>

ADSL (AWaRE DSL)~\cite{DBLP:conf/aswec/ChhetriLUVKNR18/adsl} % and see corresp RW: the most related DSLs are those in the area of automated deployment [17]. Such DSLs include Deladas [31], [32], ConfSolve [15], [33], j-ASD’s DSL [34] and MuScADeL [35], [36].
% [17]: J.-P. Arcangeli, R. Boujbel, and S. Leriche, "Automatic deployment of distributed software systems: Definitions and state of the art," Journal of Systems and Software, vol. 103, pp. 198–218, 2015
